Towards a self healing swarm through the removal of voids and anomalies

### 2018-10-01 paper.tex
Abstract Started

Swarms consist of many agents that interact using a simple set of rules that create emergent behaviours. One such behaviour makes a swarm tolerant of failures. Failures occur for may reasons; for example: resource exhaustion, component failure, or a disruption from an external event. The loss of agents reduces the size of a swarm and changes the structure in places where the agents are lost. A swarm's structure can also be irregular from an initial deployment or due to an obstacle in its path. These changes in the structure and/or size do not stop a swarm from functioning but can affect the outcome of a task to which the swarm is being applied. The paper introduces and demonstrates an emergent behaviour that can be induced into a swarm that can counter the effect of agent loss or irregular structures within a swarm. The behaviour causes concave deformities to be removed creating a healing-effect. This technique is implemented by each agent identifying it's position in relation to it's neighbours. If the agent meets a specific criteria the agent's `normal' movement is altered in such a way as to remove a gap between two of it's neighbours. These changes in direction of agents that meet the criterion cause the swarm, as a whole, to be reorganised into a more uniform structure with no internal voids.

>>>>

Swarms consist of many agents that interact using a simple set of rules that create emergent behaviours. One such behaviour makes a swarm tolerant of failures. Failures occur for many reasons, for example; resource exhaustion, component failure, or a disruption from an external event. The loss of agents reduces the size of a swarm and may create an irregular structure. A swarm's structure can also be irregular due to initial conditions, loss of agents or due to an obstacle. These changes in the structure or size do not stop a swarm from functioning but can adversely affect the efficience. This paper introduces and demonstrates emergent behaviour that can counter the effect of agent loss or irregular structures. The behaviour causes concave deformities to be removed. This technique is implemented by each agent identifying its position in relation to its neighbours. If the agent meets a defined criterion, based on the local geometry of the agent's neighbours to decide when an anomily is present, the agent's `normal' movement is altered in such a way as to remove a gap between the neighbours. These changes in direction of agents cause the swarm, as a whole, to be reorganised into a more uniform structure with no internal voids.
